---
title: "Air Pollution in Seoul"
author: "Daniel Chen"
date: "4/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Abstract

## Introduction

## Results

blah blah balh validation of input and summary

First, we load all necessary packages for this analysis.

```{r, warning = FALSE, echo = FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
```

Then we load all of the data into memory.

```{r}
measurement_summary <- data.table::fread("input/AirPollutionSeoul/Measurement_summary.csv")
measurement_info <- data.table::fread("input/AirPollutionSeoul/Original Data/Measurement_info.csv")
measurement_item_info <- data.table::fread("input/AirPollutionSeoul/Original Data/Measurement_item_info.csv")
measurement_station_info <- data.table::fread("input/AirPollutionSeoul/Original Data/Measurement_station_info.csv")
```

Then we do a quick examination of all of the datasets.

```{r}
dim(measurement_summary)
summary(measurement_summary)
plot(measurement_summary %>% select(-c(`Measurement date`, Address)))
```

```{r}
dim(measurement_info)
summary(measurement_info)
plot(measurement_summary %>% select(-c(`Measurement date`))
```


```{r}
dim(measurement_item_info)
summary(measurement_item_info)
plot(measurement_item_info %>% select(-c(`Ite`, Address)))
```


```{r}
dim(measurement_station_info)
summary(measurement_station_info)
```


## Discussion

## Acknowledgements
I would like to acknowledge Prof. Parzen and the teaching assitants of Stat 109 for teaching the course. Additionally, I would like to acknowledge bappe, Kaggle, and the Korean government for releasing this dataset.


## References
probably whatever package i need