---
title: "Air Pollution in Seoul"
author: "Daniel Chen"
date: "4/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Abstract

## Introduction

## Results

blah blah balh validation of input and summary

First, we load all necessary packages for this analysis.

```{r, warning = FALSE, echo = FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(knitr)
library(kableExtra)
```

Then we load all of the data into memory.

```{r}
measurement_summary <- data.table::fread("input/AirPollutionSeoul/Measurement_summary.csv")
measurement_info <- data.table::fread("input/AirPollutionSeoul/Original Data/Measurement_info.csv")
measurement_item_info <- data.table::fread("input/AirPollutionSeoul/Original Data/Measurement_item_info.csv")
measurement_station_info <- data.table::fread("input/AirPollutionSeoul/Original Data/Measurement_station_info.csv")
```

Then we do a quick examination of all of the datasets.

```{r}
measurement_summary_explaination <- data.frame(Variables = c("Measurement Date", "Station code", "Address", "Latitude", "Longitude", "SO2", "NO2", "O3", "CO", "PM10", "PM2.5"), Explaination = c("Date of Measurement", "Station code", "Address of monitoring station", "Latitude of station", "Longitude of station", "Average Sulfur Dioxide(ppm)", "Average NO2(ppm)", "Average O3(ppm)", "Average CO(ppm)", "Average PM10(µg/m^3)", "Average PM2.5(µg/m^3 )"))
measurement_info_explanation <- data.frame(Variables = c("Measurement Date", "Station Code", "Item Code", "Average Value", "Instrument Status"), Explanation = c("Measurement Date", "Station Code Primary key", "Item Code Primary Key", "Average value for given item code", "Status of instrument"))
measurement_item_info_explaination <- data.frame(Variables = c("Item code", "Item name", "Unit of measurement", "Good(blue)", "Normal(green)", "Bad(yellow)", "Very bad(Red)"), Explaination = c("Measurement Date", "Measured item name", "Unit of measurement", "Good value", "Normal value", "Bad value", "Very bad value"))
measurement_station_info_explaination <- data.frame(Variables = c("Station code", "Station name(district)", "Address", "Latitude", "Longitude"), Explaination = c("Station code primary key", "District name for station", "Address of station", "Latitude", "Longitude"))
```

### Dataset Summary

#### Variable Key
##### Measurement Summary
```{r, echo = FALSE}
kable(measurement_summary_explaination) %>% kable_styling()
```

#### Measurement Info
```{r, echo = FALSE}
kable(measurement_info_explanation) %>% kable_styling()
```


#### Measurement Item Info
```{r, echo = FALSE}
kable(measurement_item_info_explaination) %>% kable_styling()
```

#### Measurement Station Info
```{r, echo = FALSE}
kable(measurement_station_info_explaination) %>% kable_styling()
```



## Discussion

## Acknowledgements
I would like to acknowledge Prof. Parzen and the teaching assitants of Stat 109 for teaching the course. Additionally, I would like to acknowledge bappe, Kaggle, and the Korean government for releasing this dataset.


## References
probably whatever package i need